Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-07-09 MCQMC2022ChallengesQMCSoftwareArticle_revision_1.tex
SC: minor changes.

We draw on our collective experiences as
members of the academic QMC community, developers of open-source and commercial scientific software, and users of a wide range of scientific software as research scientists or data scientists. Many of the insights that we have gained have come through our development of the Guaranteed Automatic Integration Library (GAIL)~\cite{TonEtAl22a} in MATLAB and the Quasi-Monte Carlo Python library (ChoEtal22a)~ \cite{QMCPy2020a}.

@@

Complex integrands might be best evaluated by libraries that have no direct connection to QMC software libraries.  In the uncertainty quantification (UQ) space, the recently developed UQ and Model Bridge (UM-Bridge) \LSComment{\cite{UMBridge23}}, connects libraries that generate sequences of model parameters, $\bsx_1, \bsx_2, \ldots$ with libraries that evaluate models, $f(\bsx_1), f(\bsx_2), \ldots$   \LSComment{and optionally, their derivatives. UM-Bridge allows coupling of UQ codes to models regardless of the programming languages.}

>>>>

We draw on our collective experiences as
members of the academic QMC community, developers of open-source and commercial scientific software, and users of a wide range of scientific software as research scientists or data scientists. Many of the insights that we have gained have come through our development of the Guaranteed Automatic Integration Library (GAIL)~\SCComment{\cite{TonEtAl22a}} in MATLAB and the Quasi-Monte Carlo Python library (ChoEtal22a)~\SCComment{\cite{QMCPy2020a}}.

@@

Complex integrands might be best evaluated by libraries that have no direct connection to QMC software libraries.  In the uncertainty quantification (UQ) space, the recently developed UQ and Model Bridge (UM-Bridge) \LSComment{\cite{UMBridge23}}, connects libraries that generate sequences of model parameters, $\bsx_1, \bsx_2, \ldots$ with libraries that evaluate models, $f(\bsx_1), f(\bsx_2), \ldots$   \LSComment{, and their derivatives if applicable. UM-Bridge allows coupling of UQ codes to models regardless of the programming languages.}
